---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# reportingGuidelines

This repository contains the templates for research outputs (e.g. case reports, original articles, metaanlyses, reviews). This package can be used alone to quickly recall checklists from the EQUATOR webpage. The individual templates are made manually based on the published cheklists. 
<!-- It can be cited as follows (not yet availible):

> W. Francuzik (2018). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here (not yet availible):

> Francuzik, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-->

### How to cite

Please cite this compendium as:

> Francuzik, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/wolass/reportingGuidelines/archive/master.zip>

Or you can install this compendium as an R package, reportingGuidelines, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("wolass/reportingGuidelines")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

